Collective excitations in competing phases in two and three dimensions

### 2023-12-19 paper/main.tex
uni

Note, that all of the aforementioned operators are Hermitian. 
This means that all spectral functions need to be completely antisymmetrical, see \autoref{sec:antisymmetry_spectral}.
For this reason, we will only show the $\omega \geq 0$ in our plots. 
Additionally, we will add a small imaginary part of $10^{-5}t$ to $\omega$ in order to visualize the occurring $\delta$ peaks.

@@

The plots for the phase peak and the CDW peak in the SC phase can be found in \autoref{sec:fit_greens_functions}.
The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
We get a good agreement with the power-law behavior near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
Therefore, we conclude that the CDW peak corresponds to a $\delta$ distribution, while the phase peak is its derivative.
Note, that the latter is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
The peak itself can be interpreted as two $\delta$ distributions at $0^\pm$.

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
    \label{fig:sc_in_cdw_behavior}
\end{figure*}

With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$.
\textcolor{red}{TODO; weiter beschreiben}

>>>>

Note, that all of the aforementioned operators are Hermitian. 
This means that all spectral functions need to be completely antisymmetrical, see appendix \autoref{sec:antisymmetry_spectral}.
For this reason, we will only show the $\omega \geq 0$ in our plots. 
Additionally, we will add a small imaginary part of $10^{-5}t$ to $\omega$ in order to visualize the occurring $\delta$ peaks.

@@

The plots for the phase peak and the CDW peak in the SC phase can be found in appendix \autoref{sec:fit_greens_functions}.
The SC peak in the CDW phase behaves similarly to the latter and is therefore not shown explicitly.
We get a good agreement with the power-law behavior near the peaks with the exponents $a=-2$ (phase) and $a=-1$ (CDW), respectively.
Therefore, we conclude that the CDW peak corresponds to a $\delta$ distribution, while the phase peak is its derivative.
Note, that the latter is located at $\omega=0$ of a perfectly asymmetrical bosonic spectral function and therefore must have 0 weight.
This is given here, because $\int \delta'(\omega) \mathrm{d}\omega = 0$.
The peak itself can be interpreted as two $\delta$ distributions at $0^\pm$.

@@

\begin{figure*}
    \centering
    \includegraphics[width=.98\textwidth]{plots/sc_peak_in_cdw_position.pdf}
    \caption{The upper panels show double logarithmic plots of the positions $\omega_0$ of the SC peak in the CDW phases while the lower panels show their respective weights $w_0 = e^{b}$.
    In the upper panel, the pink markers additionally show the peak position devided by the gap $\omega_0 / \Delta_\text{CDW}$.
    The left column shows the results for the square and the right column for the simple cubic lattice at $U=-2.5t$.
    The fits are linear, i.e., $y(V) = c \ln(V/t) + d$, and the parameters are printed on the individual panels.}
    \label{fig:sc_in_cdw_behavior}
\end{figure*}

With the prevalent peaks discussed, we turn towards their behavior as the system approaches the phase transition at $V=0$ for $U=-2.5t$.
First and foremost, we investigate the peak in $\mathcal{A}_\text{Phase}(\omega)$ and $\mathcal{A}_\text{Higgs}(\omega)$ in the CDW phase.
The evolution of its position $\omega_0$ and its weight $w_0$ as $V$ is varied can be viewed double logarithmically in \autoref{fig:sc_in_cdw_behavior}.
For $V \ll 1$, the position grows with the square root of $V$. This behavior then transitions to a purely linear growth for large $V$.
Deviding $\omega_0$ by the gap $\Delta_\text{CDW}$ results in a plateau for large $V$ while leaving the square root behavior at the beginning mostly unchanged.
